\newcommand{\image}[1]{%
\ifcase#1\relax
\or
The movement of heaven is full of power.
Thus the superior man makes himself strong and untiring.
\or
The earth’s condition is receptive devotion.
Thus the superior man who has breadth of character
Carries the outer world.
\or
Clouds and thunder:
The image of Difficulty at the Beginning.
Thus the superior man
Brings order out of confusion.
\or
A spring wells up at the foot of the mountain:
The image Of YOUTH.
Thus the superior man fosters his character
By thoroughness in all that he does.
\or
Clouds rise up to heaven:
The image of WAITING.
Thus the superior man eats and drinks,
Is joyous and of good cheer.
\or
Heaven and water go their opposite ways:
The image of CONFLICT.
Thus in all his transactions the superior man
Carefully considers the beginning.
\or
In the middle of the earth is water:
The image of THE ARMY.
Thus the superior man increases his masses
By generosity toward the people.
\or
On the earth is water:
The image of HOLDING TOGETHER.
Thus the kings of antiquity
Bestowed the different states as fiefs
And cultivated friendly relations
With the feudal lords.
\or
The wind drives across heaven:
The image of THE TAMING POWER OF THE SMALL.
Thus the superior man
Refines the outward aspect of his nature.
\or
Heaven above, the lake below:
The image of TREADING.
Thus the superior man discriminates between high and low,
And thereby fortifies the thinking of the people.
\or
Heaven and earth unite: the image of PEACE.
Thus the ruler
Divides and completes the course of heaven and earth;
He furthers and regulates the gifts of heaven and earth,
And so aids the people.
\or
Heaven and earth do not unite:
The image of STANDSTILL.
Thus the superior man falls back upon his inner worth
In order to escape the difficulties.
He does not permit himself to be honored with revenue.
\or
Heaven together with fire:
The image of FELLOWSHIP WITH MEN.
Thus the superior man organizes the clans
And makes distinctions between things.
\or
Fire in heaven above:
The image of POSSESSION IN GREAT
MEASURE.
Thus the superior man curbs evil and furthers good,
And thereby obeys the benevolent will of heaven.
\or
Within the earth, a mountain:
The image of MODESTY.
Thus the superior man reduces that which is too much,
And augments that which is too little.
He weighs things and makes them equal.
\or
Thunder comes resounding out of the earth:
The image of ENTHUSIASM.
Thus the ancient kings made music
In order to honor merit,
And offered it with splendor
To the Supreme Deity,
Inviting their ancestors to be present.
\or
Thunder in the middle of the lake:
The image of FOLLOWING.
Thus the superior man at nightfall
Goes indoors for rest and recuperation.
\or
The wind blows low on the mountain:
The image of DECAY.
Thus the superior man stirs up the people
And strengthens their spirit.
\or
The earth above the lake:
The image of APPROACH.
Thus the superior man is inexhaustible
In his will to teach,
And without limits
In his tolerance and protection of the people.
\or
The wind blows over the earth:
The image of CONTEMPLATION.
Thus the kings of old visited the regions of the world,
Contemplated the people,
And gave them instruction.
\or
Thunder and lightning:
The image of BITING THROUGH.
Thus the kings of former times made firm the laws
Through clearly defined penalties.
\or
Fire at the foot of the mountain:
The image of GRACE.
Thus does the superior man proceed
When clearing up current affairs.
But he dare not decide controversial issues in this way.
\or
The mountain rests on the earth:
The image of SPLITTING APART.
Thus those above can ensure their position
Only by giving generously to those below.
\or
Thunder within the earth:
The image of THE TURNING POINT.
Thus the kings of antiquity closed the passes
At the time of solstice.
Merchants and strangers did not go about,
And the ruler
Did not travel through the provinces.
\or
Under heaven thunder rolls:
All things attain the natural state of innocence.
Thus the kings of old,
Rich in virtue, and in harmony with the time,
Fostered and nourished all beings.
\or
Heaven within the mountain:
The image of THE TAMING POWER OF
THE GREAT.
Thus the superior man acquaints himself with many sayings of antiquity
And many deeds of the past,
In order to strengthen his character thereby.
\or
At the foot of the mountain, thunder:
The image of PROVIDING
NOURISHMENT.
Thus the superior man is careful of his words
And temperate in eating and drinking.
\or
The lake rises above the trees:
The image of PREPONDERANCE OF
THE GREAT.
Thus the superior man, when he stands alone,
Is unconcerned,
And if he has to renounce the world,
He is undaunted.
\or
Water flows on uninterruptedly and reaches its goal:
The image of the Abysmal repeated.
Thus the superior man walks in lasting virtue
And carries on the business of teaching.
\or
That which is bright rises twice:
The image of FIRE.
Thus the great man, by perpetuating this brightness,
Illumines the four quarters of the world.
\or
A lake on the mountain:
The image of influence.
Thus the superior man encourages people to approach him
By his readiness to receive them.
\or
Thunder and wind: the image of
DURATION.
Thus the superior man stands firm
And does not change his direction.
\or
Mountain under heaven: the image of
RETREAT.
Thus the superior man keeps the inferior man at a distance,
Not angrily but with reserve.
\or
Thunder in heaven above:
The image of THE POWER OF THE
GREAT.
\or
Thus the superior man does not tread upon paths
That do not accord with established order.
\or
The sun rises over the earth:
The image of PROGRESS.
Thus the superior man himself
Brightens his bright virtue.
\or
The light has sunk into the earth:
The image of DARKENING OF THE LIGHT.
Thus does the superior man live with the great mass:
He veils his light, yet still shines.
\or
The image of THE FAMILY.
Thus the superior man has substance in his words
And duration in his way of life.
\or
Above, fire; below, the lake:
The image of OPPOSITION.
Thus amid all fellowship
The superior man retains his individuality.
\or
Water on the mountain:
The image of OBSTRUCTION.
Thus the superior man turns his attention to himself
And molds his character.
\or
Thunder and rain set in:
The image of DELIVERANCE.
Thus the superior man pardons mistakes
And forgives misdeeds.
\or
At the foot of the mountain, the lake:
The image of DECREASE.
Thus the superior man controls his anger
And restrains his instincts.
\or
Wind and thunder: the image of
INCREASE.
Thus the superior man:
If he sees good, he imitates it;
If he has faults, he rids himself of them.
\or
The lake has risen up to heaven:
The image of BREAK-THROUGH.
Thus the superior man
Dispenses riches downward
And refrains from resting on his virtue.
\or
Under heaven, wind:
The image of COMING TO MEET.
Thus does the prince act when disseminating his commands
And proclaiming them to the four quarters of heaven.
\or
Over the earth, the lake:
The image of GATHERING TOGETHER.
Thus the superior man renews his weapons
In order to meet the unforeseen.
\or
Within the earth, wood grows:
The image of PUSHING UPWARD.
Thus the superior man of devoted character
Heaps up small things
In order to achieve something high and great.
\or
There is no water in the lake:
The image of EXHAUSTION.
Thus the superior man stakes his life
On following his will.
\or
Water over wood: the image of THE WELL.
Thus the superior man encourages the people at their work,
And exhorts them to help one another.
\or
Fire in the lake: the image of
REVOLUTION.
Thus the superior man
Sets the calendar in order
And makes the seasons clear.
\or
Fire over wood:
The image of THE CALDRON.
Thus the superior man consolidates his fate
By making his position correct.
\or
Thunder repeated: the image of SHOCK.
Thus in fear and trembling
The superior man sets his life in order
And examines himself.
\or
Mountains standing close together:
The image of KEEPING STILL.
Thus the superior man
Does not permit his thoughts
To go beyond his situation.
\or
On the mountain, a tree:
The image of DEVELOPMENT.
Thus the superior man abides in dignity and virtue,
In order to improve the mores.
\or
Thunder over the lake:
The image of THE MARRYING MAIDEN.
Thus the superior man
Understands the transitory
In the light of the eternity of the end.
\or
Both thunder and lightning come:
The image of ABUNDANCE.
Thus the superior man decides lawsuits
And carries out punishments.
\or
Fire on the mountain:
The image of THE WANDERER.
Thus the superior man
Is clear-minded and cautious
In imposing penalties,
And protracts no lawsuits.
\or
Winds following one upon the other:
The image of THE GENTLY PENETRATING.
Thus the superior man
Spreads his commands abroad
And carries out his undertakings.
\or
Lakes resting one on the other:
The image of THE JOYOUS.
Thus the superior man joins with his friends
For discussion and practice.
\or
The wind drives over the water:
The image of DISPERSION.
Thus the kings of old sacrificed to the Lord
And built temples.
\or
Water over lake: the image of
LIMITATION.
Thus the superior man
Creates number and measure,
And examines the nature of virtue and correct conduct.
\or
Wind over lake: the image of INNER
TRUTH.
Thus the superior man discusses criminal cases
In order to delay executions.
\or
Thunder on the mountain:
The image of PREPONDERANCE OF THE
SMALL.
Thus in his conduct the superior man gives preponderance to reverence.
In bereavement he gives preponderance to grief.
In his expenditures he gives preponderance to thrift.
\or
Water over fire: the image of the condition
In AFTER COMPLETION.
Thus the superior man
Takes thought of misfortune
And arms himself against it in advance.
\or
Fire over water:
The image of the condition before transition.
Thus the superior man is careful
In the differentiation of things,
So that each finds its place.
\else OUT OF RANGE\fi
}
